---
title: "R Notebook"
output: html_notebook
editor_options: 
  Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Cmd+Shift+Enter*. 
  chunk_output_type: console
---
#---------------POSCAR/CONTCAR Editor----------------------------
Clean the store data for a new start
```{r Clean the store data for a new start}
rm(list = ls())

```
Applying all the commands together by using {} from start & end
```{r Applying all the commands together by using {} from start & end}
{
```
Import data file by click to Environment-Import Data set
or by following:
```{r Import data file}
my_data <- file.choose()
file_path <- file.path(my_data) # See the path of the imported file 
x <- readLines(my_data)# Read the data file
```
skip all the lines from line 1 to the line having "Direct"
```{r skip all the lines from line 1 to the line having "Direct"}
skip <- x[-(1:grep("Direct",x))]

```
skip <- x[-c(1:grep("Direct",x))] : with c() or without c() both gives same result. Above we remove c().
skip all lines having "0.00000000E+00" after the coordinate section
skip1 <- skip[-(grep("0.00000000E+00",skip,fixed=TRUE))] Note: "grep" is only working for the data having "0.00000000E+00" not for others.
*** trying to combine both the above skip
```{r skip all lines having "0.00000000E+00" after the coordinate section}
skip1 <- skip[-(grepl("0.00000000E+00",skip,fixed=TRUE))==0]
```
***I've got the above idea from below command: TRY to understand when have time***
skip1<-skip[Reduce("+", lapply("0.00000000E+00", grepl, skip, fixed=TRUE))==0]

*** The below command is also working, However, the better one is above one.

* invert=TRUE means skip the lines which is similar -() or -c()
* fixed = TRUE is key tag here to consder 0.00000000E+0 as it literally not by numerical sense any more.
* value = TRUE will show the all the values i.e. here lines, if value = FALSE (default case) --> It will show rows numbers only.
*grep("0.00000000E+00", x, fixed=TRUE, invert=TRUE, value=TRUE) 


```{r Converting data into table format}
y <- read.table(textConnection(skip1), sep="",colClasses = c("character"))
```
* c("character") using to avoid the T or F which is not avoided by using only the "character"

We want to freeze the Z-coordinates with selective input. Mention them as input value 
Alternatively the add on package "svDialogs" helpful to generate the dial box window
```{r Insert freeze coordinate values}
c1 <- readline(prompt="freeze coordinate (1)? ")
c2 <- readline(prompt="freeze coordinate (2)? ")
```

Add a new column next to the Z-coordinate (V3) as V4 inserting FFF or TTT

```{r Adding a new column next to the Z-cordinate with freezing values FFF or TTT}
y$V4 <- ifelse(grepl(c1, y$V3) | grepl(c2, y$V3), " F F F", " T T T")
```
* For more coordinates we can apply the following way
y$V4 <- ifelse(grepl(c1, y$V3) | grepl(c2, y$V3) | grepl(c3, y$V3) | 
grepl(c4, y$V3) | grepl(c5, y$V3) | grepl(c6, y$V3) | grepl(c7, y$V3) |
grepl(c8, y$V3) | grepl(c9, y$V3) | grepl(c10, y$V3) | grepl(c11, y$V3) |
grepl(c12, y$V3) | grepl(c13, y$V3) | grepl(c14, y$V3) | grepl(c15, y$V3) | grepl(c16, y$V3), " F F F", " T T T")

Save the new data as new POSCAR file having same formats with the header lines 
```{r Adding the header of the file before the new table data}
z<-x[(1:grep("Direct",x))]
```

```{r Mentioning File path in local computer where new data will be saved}
tmp <- "/Users/dsahu/Desktop/POSCAR_Edited"
```
Write the upper section of the table in the "POSCAR_Edited" file
```{r Write the upper section of the table in the "POSCAR_Edited" file}
cat(z, sep="\n",file = tmp)
```
* sep="\n" means show the values in line by line

```{r Add the "Selective dynamics" above "Direct" to fulfill the freezing conditions}
cat(c(z[1:7], "Selective dynamics", z[-(1:7)]), sep="\n",file = tmp)
```
*Got the idea of the above code from below trials*
*cat('Selective dynamics\n', file=tmp, append=T)
*cat(sub("Direct", "Selective dynamics\nDirect", z), sep="\n",file = tmp)

```{r Write the new data as a new table & will save as 'POSCAR_Edited' name}
write.table(y, file = tmp, append=TRUE, row.names = F, col.names = F, sep = " ",quote = FALSE)
```
**Insert the new table after the upper text in the "POSCAR_Edited" file**
*Skip the Row and Column names by using "row.names = F" & "col.names = F"
*Skip the quotation marks of characters by using quote = FALSE

```{r Terminate the overall command by ending bracket}
}

```

To run the above code together (Run>Run all chunks above)

------POSCAR/CONTCAR Editor(Elementwise Freeze)----------------------------
 Clean the store data for a new start
```{r}
rm(list = ls())
```
 
```{r As earlier above codes}
{
  my_data <- file.choose()
  file_path <- file.path(my_data)
  folder_path <- dirname(my_data) # To extract the directory/folder path
  x <- readLines(my_data)
  skip <- x[-(1:grep("Direct",x))]
  skip1 <- skip[-(grepl("0.00000000E+00",skip,fixed=TRUE))==0]
  y <- read.table(textConnection(skip1), sep="",colClasses = c("character"))
```

Since 243 first element (Cu) is present in POSCAR and we want to freeze them here 

```{r Freezing the Cu cordinates in below and rest of them will be relaxed}
pu<-y[1:243,]
  pu$V4<- "F F F"
  pus<-y[-(1:243),]
  pus$V4<- "T T T"
  puss<-rbind (pu,pus) # rbind() here adding two columns into one
```
adding header of the file before the table
"Selective dynamics" will be added on the 8th line
```{r}
z<-x[(1:grep("Direct",x))]
  z1 <- c(z[1:7], "Selective dynamics", z[8]) # Adding the text "Selective dynamics" before the text line "Direct"
```
  Location of the new File that want to save in computer
```{r}
tmp <- "/Users/dsahu/Desktop/POSCAR222"
```
After head-text "z", adding text "Selective dynamics" and separating line in order & giving file name "tmp"
```{r}
cat(z1, sep="\n",file = tmp) 
```
Write the new data Finally
```{r}
 write.table(puss, file = tmp, append=TRUE, row.names = F, col.names = F, sep = " ",quote = FALSE)
}
```
  
  
 







